---
title: "Weight of Fish"
author: "Gianna Chevez"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Perch,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="adjustedR^2")

```

### Best Models

Based on the data, the two-element model—specifically the H-W model—appears to be the most effective.

### Best Two regressor model

The data also suggests that the two best-performing regression models are the H-W models.


## Pike

```{r}
library(leaps)
regsubsets.out <-
  regsubsets(Weight ~.,
                             data=Pike,
                             nbest=1,
                             force.in=NULL,force.out=NULL,
                             method="exhaustive")
summary.out<-summary(regsubsets.out)
as.data.frame(summary.out$outmat)

```

```{r}
library(car)
subsets(regsubsets.out,statistic="adjr2",legend = "bottom",main="adjustedR^2")


```

### Best Models

The data indicates that the most effective model is the 5-element L1–L2–L3–H–W model.

### Best Two regressor model

The best two regressor model is the L1–L3 model. This means that the overall best model differs from the best two regressor model. Therefore, it is necessary to run an ANOVA test to compare them properly.

```{r}
model5 <- lm(Weight~ . ,data=Pike)
summary.lm(model5)
model2=lm(Weight~ .  -Length2-Height-Width, data=Pike)
model3=lm(Weight~ .  -Length2-Height-Width, data=Pike)
anova(model5,model2)

```

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements